Work Stress

### 2023-03-17 outputs/paper/paper.qmd
Update paper

---
title: "Work Stress"
author: 
  - Sagith Kalaichelvam
  - Youngho Kim
thanks: "Code, and data are available at: https://github.com/YoungKim164/workstress"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper discusses data from US General Social Survey, which can gather data that is linked to how people face work stress. It uses uses the original data from the survey which determines the relationships between respondent work stress levels by satisfaction, status, sectors, and work time. There will be some strong connections between the analysis and figures of the work stress. This paper will provide a strong analysis about the work stress that people are facing."
    toc: true
    number-sections: true
    colorlinks: true
    lot: false
    lof: true
bibliography: references.bib
---

@@

Even though work stress have different causes. We believe that the major cause or initial step into work stress would traffic delays. There are always traffic delays that most commuters would face almost every day. Most of these commuters are people going for work especially during rush hour time. Satisfaction rate is very important for jobs, and most people are sometimes not satisfy, its mainly due to these traffic delays. For example, if you are taking Greater Toronto Area commuters, most jobs are found in downtown Toronto, North York, and Mississauga. The GTA is going far west as Hamilton to east as Durham Region. Most of these commuters will be spending at least 1 hour of commuting to their workplace either by car or public transit [@trafficsatisfaction]. In an anonymized therapy session in 2014, a client expressed: “by the time I get home from work, I’m just, you know, after that drive, I’m just so dead, it’s like, you know, shaking and don’t want to drive anymore. I don’t want to do anything else. . . sometimes I like if there’s been lots of traffic or like if I’ve been tired and like been forcing myself to stay awake so I can get home.” [@therapy] Traffic is the main issue that we believe that is is impacting the job satisfaction rate, which is why lots of people are facing work stress. We need to find a solution that can reduce the traffic, increase job satisfaction, and if possible these can expect to reduce the work stress for everyone.

>>>>

---
title: "Work Stress"
author: 
  - Sagith Kalaichelvam
  - Youngho Kim
thanks: "Code and data are available at: https://github.com/YoungKim164/workstress"
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
format: 
  pdf:
    documentclass: article
    geometry: margin = 1in
    abstract: "This paper discusses data from US General Social Survey, which can gather data that is linked to how people face work stress. It uses uses the original data from the survey which determines the relationships between respondent work stress levels by satisfaction, status, sectors, and work time. There will be some strong connections between the analysis and figures of the work stress. This paper will provide a strong analysis about the work stress that people are facing."
    toc: true
    number-sections: true
    colorlinks: true
    lot: false
    lof: true
bibliography: references.bib
---

@@

Even though work stress have different causes. We believe that the major cause or initial step into work stress would be traffic delays, and that affects the job satisfaction rate. There are always traffic delays that most commuters would face almost every day. Most of these commuters are people going for work especially during rush hour time. Satisfaction rate is very important for jobs, and most people are sometimes not satisfy, its mainly due to these traffic delays. For example, if you are taking Greater Toronto Area commuters, most jobs are found in downtown Toronto, North York, and Mississauga. The GTA is going far west as Hamilton to east as Durham Region. Most of these commuters will be spending at least 1 hour of commuting to their workplace either by car or public transit [@trafficsatisfaction]. In an anonymized therapy session in 2014, a client expressed: “by the time I get home from work, I’m just, you know, after that drive, I’m just so dead, it’s like, you know, shaking and don’t want to drive anymore. I don’t want to do anything else. . . sometimes I like if there’s been lots of traffic or like if I’ve been tired and like been forcing myself to stay awake so I can get home.” [@therapy] Traffic is the main issue that we believe that is is impacting the job satisfaction rate, which is why lots of people are facing work stress. We need to find a solution that can reduce the traffic, increase job satisfaction, and if possible these can expect to reduce the work stress for everyone.
